Inequality in consumption

### 2017-03-13 inequality/consumption-inequality.Rmd
new inequality plot
updated inequality

@@

```{r chars_by_consumption}
ntile_zero = function(x, n) {
  out = x
  out[x > 0] = ntile(out[x > 0], n)
  out
}

@@

usage %>%
  group_by(age, sex, race, chronic, bene_id) %>%
  summarize(n_claims=sum(n_claims),
            n_days=sum(n_days)) %>%
  ungroup() %>%
  mutate(claims_group=bounds_group(n_claims, c(0, 1, 2, 5, 10, 20, 50, 100)),
         is_female=if_else(sex=='female', 1, 0),
         is_white=if_else(race=='white', 1, 0)) %>%
  group_by(claims_group) %>%
  summarize(n_beneficiaries=n(),
            mean_age=mean(age),
            percent_female=mean(is_female)*100,
            percent_white=mean(is_white)*100,
            mean_n_chronic_cond=mean(chronic),
            mean_n_claims=mean(n_claims)) %>%
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  kable
```

>>>>

```{r inequality_by_region2}
# This uses code from inequality-resistance
normalize = function(x) x / max(x)
cumrelfreq = function(df, var) {
  n = sort(df[[var]], decreasing=FALSE)
  data_frame(x=cume_dist(n), y=normalize(cumsum(n))) %>%
    group_by(x) %>%
    summarize(y=max(y))
}

#m = consumption_of('macrolide')

#x = m %>%
#  left_join(census_regions, by='state') %>%
#  group_by(region) %>%
#  do(cumrelfreq(., 'n_claims'))

#p = x %>%
#  ggplot(aes(x=x, y=y, color=region, group=region)) +
#  geom_line() + geom_point() +
#  xlab('cumulative fraction of users') +
#  ylab('cumulative fraction of drugs consumed') +
#  theme_minimal()

#show(p)
```

@@

```{r chars_by_consumption}
# load the encounters claim data
carrier_count = read_tsv('../../data/carrier_count_2011.tsv') %>%
  rename(bene_id=BENE_ID, n_carrier_dates=n_from_dates)
inpatient_count = read_tsv('../../data/inpatient_count_2011.tsv') %>%
  rename(bene_id=BENE_ID, n_inpatient_dates=n_from_dates)
outpatient_count = read_tsv('../../data/outpatient_count_2011.tsv') %>%
  rename(bene_id=BENE_ID, n_outpatient_dates=n_from_dates)

ntile_zero = function(x, n) {
  out = x
  out[x > 0] = ntile(out[x > 0], n)
  out
}

@@

na_to_zero = function(x) if_else(is.na(x), 0L, x)

usage %>%
  group_by(bene_id) %>%
  summarize(n_claims=sum(n_claims),
            n_days=sum(n_days)) %>%
  left_join(select(usage, bene_id, sex, age, race, chronic), by='bene_id') %>%
  left_join(carrier_count, by='bene_id') %>%
  left_join(outpatient_count, by='bene_id') %>%
  left_join(inpatient_count, by='bene_id') %>%
  mutate_at(vars(n_carrier_dates, n_outpatient_dates, n_inpatient_dates), na_to_zero) %>%
  mutate(claims_group=bounds_group(n_claims, c(0, 1, 2, 5, 10, 20, 50, 100)),
         is_female=if_else(sex=='female', 1, 0),
         is_white=if_else(race=='white', 1, 0)) %>%
  group_by(claims_group) %>%
  summarize(n_beneficiaries=n(),
            mean_age=mean(age),
            percent_female=mean(is_female)*100,
            percent_white=mean(is_white)*100,
            mean_n_chronic_cond=mean(chronic),
            mean_n_claims=mean(n_claims),
            mean_n_carrier_dates=mean(n_carrier_dates),
            mean_n_outpatient_dates=mean(n_outpatient_dates),
            mean_n_inpatient_dates=mean(n_inpatient_dates)) %>%
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  kable
```
